### 2014-06-30 tex/motivation.tex
updating the figures in the motivation

>>>>

\begin{figure}
\begin{tabular}[c]{l}
\begin{lstlisting}
public class LinkedList {

/** assume the linked list is valid with no cycles **/
LLNode head;
Data data0, data1, data2, data3, data4;

private class Data { Integer val; }

private class LLNode {
  protected Data elem;
  protected LLNode next; }

public static boolean contains(LLNode root, Data val) {
  LLNode node = root;
  while (true) {
    if(node.val == val)  return true;
    if(node.next == null) return false;
    node = node.next;
}}

public void run() {
if(LinkedList.contains(head, data0) && LinkedList.contains(head,data1) &&
   LinkedList.contains(head, data2) && LinkedList.contains(head, data3) &&
   LinkedList.contains(head, data4)) return;
\end{lstlisting}
\end{tabular} 
\caption{Linked list}
\label{fig:example}
\end{figure}

\begin{figure}[htb]
\scalebox{0.45}
{\includegraphics[width=563px]{../figs/time_vs_complexity.pdf}}
\caption{Time versus complexity for the linked list example}
\label{fig:tvc}
\end{figure}
